---
title: "Homework 1"
author: Yue Liu
output: github_document
---

This is my solution to HW1 

```{r}
library(tidyverse)
```


## Problem 1 

Create a data frame with the specified elements.

```{r}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
  )
```

Take the mean of each variable in my data frame.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor.

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```


## Problem 2

Load the penguins dataset.

```{r}
data("penguins", package = "palmerpenguins")
```

There are 8 variables contained in this dataset: species, island, bill length(mm), bill depth(mm), flipper mass(mm), body mass(g), sex, and year. 

Species contains three different groups: Adelie, Chinstrap, and Gentoo. 
Island also contains three different groups: Biscoe, Dream, and Torgersen. 
Bill length ranges from `r min(penguins$bill_length_mm, na.rm = TRUE)`mm to `r max(penguins$bill_length_mm, na.rm = TRUE)`mm. 
Bill depth ranges from `r min(penguins$bill_depth_mm, na.rm = TRUE)`mm to `r max(penguins$bill_depth_mm, na.rm = TRUE)`mm. 
Flipper length ranges from `r min(penguins$flipper_length_mm, na.rm = TRUE)`mm to `r max(penguins$flipper_length_mm, na.rm = TRUE)` mm.
Body mass ranges from `r min(penguins$body_mass_g, na.rm = TRUE)`g to `r max(penguins$body_mass_g, na.rm = TRUE)`g.
Sex contains 2 groups: female and male.
Year ranges from 2007 to 2009.

The penguins dataset contains `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

Generates a scatterplot of flipper length vs bill length.

```{r scatterplot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() + labs(title = "Scatterplot of Flipper Length vs Bill Length",
       x = "Bill Length (mm)", y = "Flipper Length (mm)")
ggsave("scatterplot.pdf")
```

